
\documentclass[11pt]{article}

\usepackage{verbatim}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{latexsym}
\usepackage{epsfig}
\usepackage{color}
\setlength{\oddsidemargin}{0.35in}
\setlength{\evensidemargin}{0.35in}
\setlength{\topmargin}{-1cm}

\hoffset-1in
\voffset+0.1in
\if@twoside\oddsidemargin25mm
\evensidemargin25mm\marginparwidth25mm
\else
\oddsidemargin25mm\evensidemargin25mm\marginparwidth25mm\fi%
\textwidth 17cm
\textheight 45\baselineskip


\input{texdefs} 

\begin{document}


Let $x^m, y^m$ and $z^m$ be three (independent) vectors in four
dimensions. The tensor that we are considering, 
\equ{
A^{mnp} = \frac 12 \Big( x^m \, y^n - x^n \, y^m \Big) z^p~, 
\labl{expl}
}
has $6 \cdot 4 = 24$ components. But not all of them are relevant when
contracted with the operator in our theory. This means that we are
looking for the most general tensor $C^{mnp}$ constructed from
$A^{Pmnp}$ such that: 
\equ{
C^{mnp}\, \ge_{mnpq} = 0~, 
\qquad 
C^{mnp}\, \get_{np} = 0~. 
\labl{cond}
}
Since these are two vector equations, $C^{mnp}$ has $24 - 4-4=16$ 
independent components. 


Before constructing this tensor explicitly, we investigate the
symmetry properties of a tensor 
\equ{
B^{mnp} = A^{mnp} + \ge^{mnpq} N_q~,
}
with $N_q$ chosen such that the first condition in \eqref{cond} is
satisfied. Using the explicit form of $A^{mnp}$ in \eqref{expl}, we
find that $B^{mnp}$ takes the form
\equ{
B^{mnp} = \frac 16 \Big[ 
2 \Big( x^m \, y^n - x^n \, y^m \Big) z^p 
+ \Big( x^m \, y^p - x^p \, y^m \Big) z^n
+ \Big( x^p \, y^n - x^n \, y^p \Big) z^m 
\Big]~. 
}
Clearly, $B^{mnp}$ is not symmetric in the last two indices: 
$B^{mpn} \neq B^{mnp}\,$. So our assumption that we could obtain the
irreducible representation by symmetrization was wrong. 


To construct the tensor $C^{mnp}$ we proceed as follows. Notice that
$C^{mnp}$ has $16 =4\cdot 4$ components, therefore one might expect
one needs two vectors $x^m$ and $y^m$ to parameterize it. Indeed, 
consider the tensors
\equ{
\arry{rcl}{
C_\pm^{mnp} (x, y) &= & \dsp 
\frac 12 \Big( x^m \, y^n - x^n \, y^m \Big) x^p 
\mp  \frac 12 \Big( x^m \, y^n - x^n \, y^m \Big) y^p 
\\[2ex] & & \dsp 
+ \frac {(x \mp y) \cdot y}6
\Big( \get^{mp} \, x^n - \get^{np}\, x^m \Big) 
- \frac {(x \mp y) \cdot x}6 
\Big( \get^{mp} \, y^n - \get^{np}\, y^m \Big) 
~. 
}
}
It is not difficult to check that they satisfy both conditions of
\eqref{cond}. Because under the interchange of $x$ and $y$ we find 
\equ{
C_\pm^{mnp}(y,x) = \pm\, C_\pm^{mnp}(x,y)~, 
} 
$C_+^{mnp}$ and $C_-^{mnp}$ have $10$ and $6$ components,
respectively. 



\end{document} 



